---
title: "Summary statistics, vep data"
output:
  html_document:
    df_print: paged
---

```{r, include = FALSE}
#  print summary table
summaryTable <- function(dvColumn, groupColumn) {
  m_AM <- mean(dvColumn[groupColumn=='AM'], na.rm=T)
  sd_AM <- sd(dvColumn[groupColumn=='AM'], na.rm=T)
  m_BD <- mean(dvColumn[groupColumn=='BD'], na.rm=T)
  sd_BD <- sd(dvColumn[groupColumn=='BD'], na.rm=T)
  m_NS <- mean(dvColumn[groupColumn=='NS'], na.rm=T)
  sd_NS <- sd(dvColumn[groupColumn=='NS'], na.rm=T)
  datatab <- matrix(data = c(m_NS, sd_NS, m_AM, sd_AM, m_BD, sd_BD), nrow=3, byrow = TRUE)
  colnames(datatab) <- c('M', 'SD')
  rownames(datatab) <- c('NS', 'AM', 'BD')
  return(datatab)
}

printMeansAndSDs <- function(dvColumn, groupColumn, roundto) {
  m_AM <- mean(dvColumn[groupColumn=='AM'], na.rm=T)
  sd_AM <- sd(dvColumn[groupColumn=='AM'], na.rm=T)
  m_BD <- mean(dvColumn[groupColumn=='BD'], na.rm=T)
  sd_BD <- sd(dvColumn[groupColumn=='BD'], na.rm=T)
  m_NS <- mean(dvColumn[groupColumn=='NS'], na.rm=T)
  sd_NS <- sd(dvColumn[groupColumn=='NS'], na.rm=T)
  
  output1 <- paste0('Control: ', round(m_NS,roundto), ' (', round(sd_NS,roundto), ')')
  output2 <- paste0('Amblyopia: ', round(m_AM,roundto), ' (', round(sd_AM,roundto), ')')
  output3 <- paste0('Strabismus with equal acuity: ', round(m_BD,2), ' (', round(sd_BD,roundto), ')')
  return(list(output1,output2,output3))
}

printTTestResult <- function(dvColumn, groupColumn) {
  # t(14.52) = 4.79, p < 0.0001; Glass’s ∆ = 5.10
  t_result <- t.test(dvColumn[groupColumn=='AM'], dvColumn[groupColumn=='NS'])
  gd <- glass_delta(dvColumn[groupColumn=='AM'], dvColumn[groupColumn=='NS'])
  
  if (t_result$p.value < 0.0001) {
    pstring <- 'p < 0.0001'
  } else {
    pstring <- paste('p =', signif(t_result$p.value,2))
  }

  out1 <- paste0("t(", round(t_result$parameter,1),
         ") = ", abs(round(t_result$statistic,2)),
         ", ", pstring,  
         "; Glass's ∆ = ", abs(round(gd$Glass_delta,2)))
  return(list(out1, pstring))
}

printAnovaByEyeTable <- function(data, selectCols) {
  #  example selectCols = c('uAE', 'uFE')
  # assumes your condition/group var is called group

data_subset <- subset(data, select = c('sID', 'group', selectCols))

#  subset out the BD data
data_subset <- subset(data_subset, group != 'BD')
data_subset$group <- droplevels(data_subset$group)

data_long <- gather(data_subset, eye, value, 3:4)
data_long$sID <- factor(data_long$sID)
data_long$eye <- factor(data_long$eye)

res.aov <- anova_test(data=data_long, dv=value, wid = sID, between = group, within = eye)
tmp <- get_anova_table(res.aov)

posthoc1 <- data_long %>% group_by(eye) %>%
  anova_test(dv = value, wid = sID, between = group) %>%
  get_anova_table() %>%
  adjust_pvalue(method = 'bonferroni')

indGrp <- which(tmp[,'Effect'] == 'group')
indEye <- which(tmp[,'Effect'] == 'eye')
indIxn <- which(tmp[,'Effect'] == 'group:eye')


# build text output
if (tmp[indGrp,'p'] < 0.05) {
  # sig
  strGrp <- 'Main effect of group'
} else {
  # non-sig
  strGrp <- 'No main effect of group'
}
  
  if (tmp[indGrp,'p'] < 0.0001) {
    pGrp <- 'p < 0.0001'
  } else {
    pGrp <- paste('p =', signif(tmp[indGrp,'p'],2))
  }

if (tmp[indEye,'p'] < 0.05) {
  # sig
  strEye <- 'main effect of eye'
} else {
  # non-sig
  strEye <- 'no main effect of eye'
}
  
  if (tmp[indEye,'p'] < 0.0001) {
    pEye <- 'p < 0.0001'
  } else {
    pEye <- paste('p =', signif(tmp[indEye,'p'],2))
  }


if (tmp[indIxn,'p'] < 0.05) {
  # sig
  strIxn <- 'a significant group by eye interaction'
} else {
  # non-sig
  strIxn <- 'no group by eye interaction'
}
  
  if (tmp[indIxn,'p'] < 0.0001) {
    pIxn <- 'p < 0.0001'
  } else {
    pIxn <- paste('p =', signif(tmp[indIxn,'p'],2))
  }


# posthoc: eye 1
if (posthoc1$p[1] < 0.05) {
  # sig
  strPh1 <- paste('difference in', selectCols[1])
} else {
  # non-sig
  strPh1 <- paste('no difference in', selectCols[1])
}

if (posthoc1$p[1] < 0.0001) {
    pPh1 <- 'p < 0.0001'
  } else {
    pPh1 <- paste('p =', signif(posthoc1$p[1],2))
}


# posthoc: eye 2
if (posthoc1$p[2] < 0.05) {
  # sig
  strPh2 <- paste('difference in', selectCols[2])
} else {
  # non-sig
  strPh2 <- paste('no difference in', selectCols[2])
}

if (posthoc1$p[2] < 0.0001) {
    pPh2 <- 'p < 0.0001'
  } else {
    pPh2 <- paste('p =', signif(posthoc1$p[2],2))
}


out1 <- paste0(strGrp, ", F(", tmp[indGrp,'DFn'], ",", tmp[indGrp,'DFd'],
               ") = ", round(tmp[indGrp,'F'],2), ", ", pGrp, ",
               genEtaSq = ", signif(tmp[indGrp, 'ges'],2), ";")

out2 <- paste0(strEye, ", F(", tmp[indEye,'DFn'], ",", tmp[indEye,'DFd'],
               ") = ", round(tmp[indEye,'F'],2), ", ", pEye,
               ", genEtaSq = ", signif(tmp[indEye, 'ges'],2), ";")

out3 <- paste0(strIxn, ", F(", tmp[indIxn,'DFn'], ",", tmp[indIxn,'DFd'],
               ") = ", round(tmp[indIxn,'F'],2), ", ", pIxn, ",
               genEtaSq = ", signif(tmp[indIxn, 'ges'],2), ".")

out4 <- paste0("Simple main effects: ", strPh1, ",
               F(", posthoc1[1,'DFn'], ",", posthoc1[1,'DFd'],
               ") = ", round(posthoc1[1,'F'],2), ", ", pPh1,
               ", genEtaSq = ", signif(posthoc1[1, 'ges'],2), ";")


out5 <- paste0(strPh2, ", F(", posthoc1[2,'DFn'], ",", posthoc1[2,'DFd'],
               ") = ", round(posthoc1[2,'F'],2), ", ", pPh2,
               ", genEtaSq = ", signif(posthoc1[2, 'ges'],2), ".")

returnStr <- paste(out1,out2,out3,out4,out5)
return(list(returnStr, pGrp, pEye, pIxn, pPh1, pPh2))
}

printRegressionResults <-function(dvCol,groupCol,modelParamCol){
  # output order: group alone, parameter alone, parameter after controlling for grp
  mod_group <- lm(dvCol ~ groupCol)
  mod_param <- lm(dvCol ~ modelParamCol)
  mod_group_param <- lm(dvCol ~ groupCol + modelParamCol)
  
smod_group <- summary(mod_group)
smod_param <- summary(mod_param)
smod_group_param <- Anova(mod_group_param)

# format pstring

p_group <-   pf(smod_group$fstatistic[1],
                smod_group$fstatistic[2],
                smod_group$fstatistic[3], lower.tail = F)
if (p_group < 0.0001) {
p1 <- 'p < 0.0001'
} else {
  p1 <- paste('p =', signif(p_group,2))
}
if (p_group < 0.05) {
  p1 <- paste(p1, '*')
}


p_param <-   pf(smod_param$fstatistic[1],
                smod_param$fstatistic[2],
                smod_param$fstatistic[3], lower.tail = F)
if (p_param < 0.0001) {
p2 <- 'p < 0.0001'
} else {
  p2 <- paste('p =', signif(p_param,2))
}
if (p_param < 0.05) {
  p2 <- paste(p2, '*')
}



p_group_param <- smod_group_param$P[2]

if (p_group_param < 0.0001) {
p3 <- 'p < 0.0001'
} else {
  p3 <- paste('p =', signif(p_group_param,2))
}
if (p_group_param < 0.05) {
  p3 <- paste(p3, '*')
}


out1 <- paste0("F(", smod_group$fstatistic["numdf"], ",",
              smod_group$fstatistic["dendf"], 
              ") = ", round(smod_group$fstatistic['value'],2),
              ", ", p1)
out2 <- paste0("F(", smod_param$fstatistic["numdf"],",",
               smod_param$fstatistic["dendf"], 
              ") = ", round(smod_param$fstatistic['value'],2),
              ", ", p2)

out3 <-  paste0("F(", smod_group_param$Df[2],",",
                smod_group_param$Df[3], 
              ") = ", round(smod_group_param$F[2],2),
              ", ", p3)
return(list(out1,out2,out3))
}

printCorrelByGroup <- function(x, y, groupCol) {
  allCor <- cor(x,y)
  corAM <- cor(x[groupCol == 'AM'], y[groupCol == 'AM'])
  corBD <- cor(x[groupCol == 'BD'], y[groupCol == 'BD'])
  corNS <- cor(x[groupCol == 'NS'], y[groupCol == 'NS'])
  
  out <- paste0('Everyone: r = ',
                round(allCor,2), 
    '; r~amblypoia~ = ', round(corAM,2),
    ', r~strabismus~ = ', round(corBD,2),
    ', r~control~ = ', round(corNS,2))
  
  return(out)
}

correlPlot <- function(x, y, group, legendTF, xlab, ylab, xlim, ylim) {
  
  # Get coefficient for the plot
  mod_full <- lm(y ~ x)           
  xycor <- round(cor(x, y),2)
  
  # plot the x,y data
  plot(x,y,                 
       xlab = xlab,
       ylab = ylab,
       xlim = xlim,
       ylim = ylim,
       type = 'n',
       cex = 0.8,
       cex.lab = 0.8,
       cex.axis = 0.8
  )
  
  grid(nx = NULL, ny = NULL)
  
  # Add the unity line
  abline(a=0, b=1, col='black')

  # add points
  
  # add amblyopia
  points(x[group == 'AM'], y[group == 'AM'],
         pch = pchAM, col=colAM)
  
  # add strab
  points(x[group == 'BD'], y[group == 'BD'],
         pch = pchBD, col=colBD)
  
  # add control
  points(x[group == 'NS'], y[group == 'NS'],
         pch = pchNS, col=colNS)
  
  # add means
  t.am.x <- t.test(x[group == 'AM'])
  t.am.y <- t.test(y[group == 'AM'])
  t.bd.x <- t.test(x[group == 'BD'])
  t.bd.y <- t.test(y[group == 'BD'])
  t.ns.x <- t.test(x[group == 'NS'])
  t.ns.y <- t.test(y[group == 'NS'])
  
  m.am.x <- t.am.x$estimate
  m.am.y <- t.am.y$estimate
  m.bd.x <- t.bd.x$estimate
  m.bd.y <- t.bd.y$estimate
  m.ns.x <- t.ns.x$estimate
  m.ns.y <- t.ns.y$estimate
  
  se.am.x <- t.am.x$stderr
  se.am.y <- t.am.y$stderr
  se.bd.x <- t.bd.x$stderr
  se.bd.y <- t.bd.y$stderr
  se.ns.x <- t.ns.x$stderr
  se.ns.y <- t.ns.y$stderr
  
  drawlinesX <- c(m.am.x - se.am.x, m.am.x + se.am.x, NA,
                  m.bd.x - se.bd.x, m.bd.x + se.bd.x, NA,
                  m.ns.x - se.ns.x, m.ns.x + se.ns.x, NA,
                  m.am.x, m.am.x, NA,
                  m.bd.x, m.bd.x, NA,
                  m.ns.x, m.ns.x)
  
  drawlinesY <- c(m.am.y, m.am.y, NA,
                  m.bd.y, m.bd.y, NA,
                  m.ns.y, m.ns.y, NA,
                  m.am.y - se.am.y, m.am.y + se.am.y, NA,
                  m.bd.y - se.bd.y, m.bd.y + se.bd.y, NA,
                  m.ns.y - se.ns.y, m.ns.y + se.ns.y)
  
  lines(drawlinesX, drawlinesY, col='black', lwd=1.5)
  
  points(m.am.x, m.am.y, 
         pch = c(pchAM), 
         col = c(colAM_solid),
         cex = 1.5)
  
  points(m.bd.x, m.bd.y, 
         pch = c(pchBD), 
         col = c(colBD_solid),
         cex = 1.5)
  
  points(m.ns.x, m.ns.y, 
         pch = c(pchNS), 
         col = c(colNS_solid),
         cex = 1.5)
 
  if (legendTF == TRUE) {
    legendloc <- 'bottomright'
    legend(legendloc, legend=c('amblyopia', 'strabismus', 'control'),
           col=c(colAM_solid, colBD_solid, colNS_solid),
           pch=c(pchAM, pchBD, pchNS),
           bty='n',
           inset = c(0.05, 0),
           y.intersp = 0.7,
           lwd=c(1,1), lty=c(2,3,4), cex=0.7)
  }
}


## colours & pchs

grey_transp <- rgb(.1, .1, .1, .1)

colAM <- rgb(1,0,0, alpha = 0.6)
colNS <- rgb(0,0,1, alpha = 0.6)
colBD <- rgb(0,.5, 0, alpha = 0.6)
pchAM <- 16
pchNS <- 18
pchBD <- 15

colAM_solid <- rgb(1,0,0)
colNS_solid <- rgb(0,0,1)
colBD_solid <- rgb(0,.5,0)

## Plots

stripchart_w_means <- function(DV, group, strDV, ylimits) {
  # DV = column for DV (eg data$delay)
  # group = column for group (eg data$group)
  # strDV = string, DV name (for plot)
  # ylimits = c(min, max)
  
  # deal with missing values
  if (any(is.na(DV))) {
    ind <- !is.na(DV)
    DV <- DV[ind]
    group <- group[ind]
  }
  
  desc_matrix <- groupMeans(DV, group) # helper function below
  
  # rounding for stripcharts - allows prettier stacking
  if (strDV == 'kAE') {
  DV <- round(DV/2,2)*2
  } else if (strDV == 'sigma') {
    DV <- round(DV*2,1)/2
  } else if (strDV == 'intercept') {
    DV <- round(DV,2)
  } else if (strDV == 'calib. err (indiv. trials)') {
    DV <- round(DV, 3)
  } else if (strDV == 'calib. err (mean trials)') {
    DV <- round(DV, 3)
  } else  {
    DV <- round(DV,1) 
  }
  
  # plot
  stripchart(DV ~ group,
             group.names = c(' ', ' ', ' '),
             xlab = ' ',
             ylab = paste(strDV, '[SE]'),
             xlim = c(0.5,3.5),
             ylim = ylimits,
             method = 'stack', offset = 0.5,
             pch = c(pchAM, pchBD, pchNS),
             col = c(colAM, colBD, colNS),
             bg = grey_transp, vertical=TRUE,
             cex.axis=1.2, cex.lab = 1.2) 
  
  grid(nx = NA, ny = NULL)
  
  offset <- 0.2
  drawlinesX <- c(1, 1, NA, 2, 2, NA, 3, 3) - offset
  drawlinesY <- c(desc_matrix[1,1] + desc_matrix[1,2],
                  desc_matrix[1,1] - desc_matrix[1,2], NA,
                  desc_matrix[2,1] + desc_matrix[2,2],
                  desc_matrix[2,1] - desc_matrix[2,2], NA,
                  desc_matrix[3,1] + desc_matrix[3,2],
                  desc_matrix[3,1] - desc_matrix[3,2])
  
  lines(drawlinesX, drawlinesY, col="black", lwd=3)
  
  points(c(1,2,3)-offset , desc_matrix[,1], 
         pch = c(pchAM, pchBD, pchNS), 
         col = c(colAM_solid, colBD_solid, colNS_solid),
         cex = 1.5)
  
  mtext('amblyopia', side = 1, at=1, font=1, line = 1, cex=.9, col=colAM_solid)
  mtext('strabismus', side = 1, at=2, font=1, line=1,cex=.9, col=colBD_solid)
  mtext('control', side = 1, at=3, font=1, line=1,cex=.9, col=colNS_solid)
}

stripchart_w_means_byeye <- function(DV_AE, DV_FE, group_AE, group_FE, strDV, ylimits) {
  # DV_AE = column for DV, amblyopic eye (eg data$uAE)
  # DV_FE = column for DV, fellow eye (eg data$uFE)
  # group = column for group (eg data$group)
  # strDV = string, DV name (for plot)
  # ylimits = c(min, max)
  
  # missing data checks
  
  if (any(is.na(DV_AE))) {
    ind <- !is.na(DV_AE)
    DV_AE <- DV_AE[ind]
    group_AE <- group_AE[ind]
  }
  
  if (any(is.na(DV_FE))) {
    ind <- !is.na(DV_FE)
    DV_FE <- DV_FE[ind]
    group_FE <- group_FE[ind]
  }
  
  group_AE <- paste0(group_AE, ' (AE)')
  group_FE <- paste0(group_FE, ' (FE)')
  
  desc_matrix <- groupMeans_byEye(c(DV_AE, DV_FE), c(group_AE, group_FE))
  
  # pretty-ify the stack for stripchart function
  
  if (strDV == 'u') {
    # round to the nearest 10ths
    xvar = round(c(DV_AE, DV_FE),1)
  } else {
    # round to the nearest even 
    xvar <- round(c(DV_AE, DV_FE)*2,1)/2
   }
     
  
  # plot
  stripchart(xvar ~ c(group_AE, group_FE),
             group.names = c('AE', 'FE', 'AE', 'FE', 'AE', 'FE'),
             xlab = ' ',
             ylab = paste(strDV, '[SE]'),
             xlim = c(0.5,6.5),
             ylim = ylimits,
             method = 'stack', offset = 0.4,
             pch = c(pchAM, pchAM, pchBD, pchBD, pchNS, pchNS),
             col = c(colAM, colAM, colBD, colBD, colNS, colNS),
             bg=grey_transp, vertical=TRUE,
             cex.axis=1.2, cex.lab=1.2) 
  
  grid(nx = NA, ny = NULL)
  
  offset <- 0.2
  drawlinesX <- c(1, 1, NA, 2, 2, NA, 
                  3, 3, NA, 4, 4, NA,
                  5, 5, NA, 6, 6) - offset
  drawlinesY <- c(desc_matrix[1,1] + desc_matrix[1,2],
                  desc_matrix[1,1] - desc_matrix[1,2], NA,
                  desc_matrix[2,1] + desc_matrix[2,2],
                  desc_matrix[2,1] - desc_matrix[2,2], NA,
                  desc_matrix[3,1] + desc_matrix[3,2],
                  desc_matrix[3,1] - desc_matrix[3,2], NA,
                  desc_matrix[4,1] + desc_matrix[4,2],
                  desc_matrix[4,1] - desc_matrix[4,2], NA,
                  desc_matrix[5,1] + desc_matrix[5,2],
                  desc_matrix[5,1] - desc_matrix[5,2], NA,
                  desc_matrix[6,1] + desc_matrix[6,2],
                  desc_matrix[6,1] - desc_matrix[6,2])
  
  lines(drawlinesX, drawlinesY, col="black", lwd=3)
  
  points(c(1,2,3,4,5,6)-offset , desc_matrix[,1],
         pch = c(pchAM, pchAM, pchBD, pchBD, pchNS, pchNS),
         col = c(colAM_solid, colAM_solid,
                 colBD_solid, colBD_solid,
                 colNS_solid, colNS_solid),
         cex = 1.2)
  
  
  mtext('amblyopia', side = 1, at=1.5, font=1, line = 2, cex=1, col=colAM_solid)
  mtext('strabismus', side = 1, at=3.5, font=1, line=2,cex=1, col=colBD_solid)
  mtext('control', side = 1, at=5.5, font=1, line=2,cex=1, col=colNS_solid)
}


RegressPlot <- function(x, y, group, legendTF, xlab, ylab, xlim, ylim) {
  
  group <- relevel(group, 'NS') # normally-sighted folks are the ref
  mod_all <-lm(y ~ group + x)
  coefs_all <- coef(mod_all)
  
  b_all <- coefs_all[4]
  a_NS <- coefs_all[1]
  a_AM <- coefs_all[1] + coefs_all[2]
  a_BD <- coefs_all[1] + coefs_all[3]
  
  # plot the x,y data
  plot(x,y,                 
       xlab = xlab,
       ylab = ylab,
       xlim = xlim,
       ylim = ylim,
       type = 'n',
       cex = 1,
       cex.lab = 1.2,
       cex.axis = 1
  )
  
  grid(nx = NULL, ny = NULL)
  
  # Add the correlation lines
  
  # amblyopia
  abline(a=a_AM, b = b_all, 
         lwd=1.5, 
         lty=2, 
         col=colAM_solid)   
  
  # strab
  abline(a=a_BD, b=b_all, 
         lwd=1.5, 
         lty=3, 
         col=colBD_solid)   
  
  # control
  abline(a = a_NS, b = b_all, 
         lwd=1.5, 
         lty=4, 
         col=colNS_solid)   
  
  # add points
  
  # add amblyopia
  points(x[group == 'AM'], y[group == 'AM'],
         pch = pchAM, col=colAM)
  
  # add strab
  points(x[group == 'BD'], y[group == 'BD'],
         pch = pchBD, col=colBD)
  
  # add control
  points(x[group == 'NS'], y[group == 'NS'],
         pch = pchNS, col=colNS)
  
  if (legendTF == TRUE) {
    legendloc <- 'bottomleft'
    legend(legendloc, legend=c('amblyopia', 'strabismus', 'control'),
           col=c(colAM_solid, colBD_solid, colNS_solid),
           pch=c(pchAM, pchBD, pchNS),
           bty='n',
           inset = c(0.05, 0),
           y.intersp = 0.7,
           lwd=c(1,1), lty=c(2,3,4), cex=0.7)
  }
}


correlPlot <- function(x, y, group, legendTF, xlab, ylab, xlim, ylim) {
  
  # Get coefficient for the plot
  mod_full <- lm(y ~ x)           
  xycor <- round(cor(x, y),2)
  
  # plot the x,y data
  plot(x,y,                 
       xlab = xlab,
       ylab = ylab,
       xlim = xlim,
       ylim = ylim,
       type = 'n',
       cex = 0.8,
       cex.lab = 0.8,
       cex.axis = 0.8
  )
  
  grid(nx = NULL, ny = NULL)
  
  # Add the unity line
  abline(a=0, b=1, col='black')

  # add points
  
  # add amblyopia
  points(x[group == 'AM'], y[group == 'AM'],
         pch = pchAM, col=colAM)
  
  # add strab
  points(x[group == 'BD'], y[group == 'BD'],
         pch = pchBD, col=colBD)
  
  # add control
  points(x[group == 'NS'], y[group == 'NS'],
         pch = pchNS, col=colNS)
  
  # add means
  t.am.x <- t.test(x[group == 'AM'])
  t.am.y <- t.test(y[group == 'AM'])
  t.bd.x <- t.test(x[group == 'BD'])
  t.bd.y <- t.test(y[group == 'BD'])
  t.ns.x <- t.test(x[group == 'NS'])
  t.ns.y <- t.test(y[group == 'NS'])
  
  m.am.x <- t.am.x$estimate
  m.am.y <- t.am.y$estimate
  m.bd.x <- t.bd.x$estimate
  m.bd.y <- t.bd.y$estimate
  m.ns.x <- t.ns.x$estimate
  m.ns.y <- t.ns.y$estimate
  
  se.am.x <- t.am.x$stderr
  se.am.y <- t.am.y$stderr
  se.bd.x <- t.bd.x$stderr
  se.bd.y <- t.bd.y$stderr
  se.ns.x <- t.ns.x$stderr
  se.ns.y <- t.ns.y$stderr
  
  drawlinesX <- c(m.am.x - se.am.x, m.am.x + se.am.x, NA,
                  m.bd.x - se.bd.x, m.bd.x + se.bd.x, NA,
                  m.ns.x - se.ns.x, m.ns.x + se.ns.x, NA,
                  m.am.x, m.am.x, NA,
                  m.bd.x, m.bd.x, NA,
                  m.ns.x, m.ns.x)
  
  drawlinesY <- c(m.am.y, m.am.y, NA,
                  m.bd.y, m.bd.y, NA,
                  m.ns.y, m.ns.y, NA,
                  m.am.y - se.am.y, m.am.y + se.am.y, NA,
                  m.bd.y - se.bd.y, m.bd.y + se.bd.y, NA,
                  m.ns.y - se.ns.y, m.ns.y + se.ns.y)
  
  lines(drawlinesX, drawlinesY, col='black', lwd=1.5)
  
  points(m.am.x, m.am.y, 
         pch = c(pchAM), 
         col = c(colAM_solid),
         cex = 1.5)
  
  points(m.bd.x, m.bd.y, 
         pch = c(pchBD), 
         col = c(colBD_solid),
         cex = 1.5)
  
  points(m.ns.x, m.ns.y, 
         pch = c(pchNS), 
         col = c(colNS_solid),
         cex = 1.5)
 
  if (legendTF == TRUE) {
    legendloc <- 'bottomright'
    legend(legendloc, legend=c('amblyopia', 'strabismus', 'control'),
           col=c(colAM_solid, colBD_solid, colNS_solid),
           pch=c(pchAM, pchBD, pchNS),
           bty='n',
           inset = c(0.05, 0),
           y.intersp = 0.7,
           lwd=c(1,1), lty=c(2,3,4), cex=0.7)
  }
}


## Helpful lil functions

groupMeans <- function(DV, group) {
  # DV = column for DV (eg data$delay)
  # group = column for group (eg data$group)
  
  # get means and SEs
  t_AM <- t.test(DV[group == 'AM'])
  desc_AM <- c(t_AM$estimate, t_AM$stderr, t_AM$conf.int)
  
  t_BD <- t.test(DV[group == 'BD'])
  desc_BD <- c(t_BD$estimate, t_BD$stderr, t_BD$conf.int)
  
  # workaround (error if controls have all same [eg stereo] values)
  t_NS <- try(t.test(DV[group == 'NS']))
  desc_NS <- c(t_NS$estimate, t_NS$stderr, t_NS$conf.int)
  
  descriptives <- rbind(desc_AM, desc_BD, desc_NS)
  rownames(descriptives) <- c('AM', 'BD', 'NS')
  colnames(descriptives) <- c('mean', 'stderr', '95ci-low', '95ci-upp')
  
  return(descriptives)
}

groupMeans_byEye <- function(DV, group) {
  
  # get means and SEs
  t_AM_AE <- t.test(DV[group == 'AM (AE)'])
  desc_AM_AE <- c(t_AM_AE$estimate, t_AM_AE$stderr, t_AM_AE$conf.int)
  t_AM_FE <- t.test(DV[group == 'AM (FE)'])
  desc_AM_FE <- c(t_AM_FE$estimate, t_AM_FE$stderr, t_AM_FE$conf.int)
  
  
  # workaround for controls having stereo values that are all the same (good stereo) is needed
  
  t_NS_AE <- try(t.test(DV[group == 'NS (AE)']))
  desc_NS_AE <- c(t_NS_AE$estimate, t_NS_AE$stderr, t_NS_AE$conf.int)
  
  t_NS_FE <- try(t.test(DV[group == 'NS (FE)']))
  desc_NS_FE <- c(t_NS_FE$estimate, t_NS_FE$stderr, t_NS_FE$conf.int)
  
  
  # 
  t_BD_AE <- t.test(DV[group == 'BD (AE)'])
  desc_BD_AE <- c(t_BD_AE$estimate, t_BD_AE$stderr, t_BD_AE$conf.int)
  t_BD_FE <- t.test(DV[group == 'BD (FE)'])
  desc_BD_FE <- c(t_BD_FE$estimate, t_BD_FE$stderr, t_BD_FE$conf.int)
  
  
  descriptives <- rbind(desc_AM_AE, desc_AM_FE,
                        desc_BD_AE, desc_BD_FE,
                        desc_NS_AE, desc_NS_FE)
  rownames(descriptives) <- c('AM (AE)','AM (FE)', 
                              'BD (AE)', 'BD (FE)',
                              'NS (AE)', 'NS (FE)')
  colnames(descriptives) <- c('mean', 'stderr', '95ci-low', '95ci-upp')
  
  return(descriptives)
}


```


```{r, include=FALSE}
# set working directory:
# (note for .Rmd make sure this is same place the current file is saved)
# setwd("/Users/bear/Downloads/dynamic_contrast/analysis_vep")

library('psych')
library('tidyr')
library('rstatix')
library('lm.beta')
library('kableExtra')
library('effectsize')

csvModelFitsPath <- file.path('..', 'fitdata_vep', 'vep_fits.csv')
data <- read.csv(csvModelFitsPath)
data$group <- as.factor(data$group)

```


## Model parameter means

```{r, include=FALSE}

#delay_means <- printMeansAndSDs(data$delay, data$group, 2)
#delay_ttest <- printTTestResult(data$delay, data$group)

intercept_means <- printMeansAndSDs(data$intercept, data$group, 2)
intercept_ttest <- printTTestResult(data$intercept, data$group)

slope_means <- printMeansAndSDs(data$slope, data$group, 2)
slope_ttest <- printTTestResult(data$slope, data$group)

joyCalErrMean_means <- printMeansAndSDs(data$joyCalErrMean, data$group, 3)
joyCalErrMean_ttest <- printTTestResult(data$joyCalErrMean, data$group)

joyCalErrInd_means <- printMeansAndSDs(data$joyCalErrInd, data$group, 3)
joyCalErrInd_ttest <- printTTestResult(data$joyCalErrInd, data$group)


kae_means <- printMeansAndSDs(data$kAE, data$group, 2)
kae_ttest <- printTTestResult(data$kAE, data$group)

#sigma_means <- printMeansAndSDs(data$sigma, data$group, 2)
#sigma_ttest <- printTTestResult(data$sigma, data$group)

mse_means <- printMeansAndSDs(data$softmaxErr, data$group, 3)
mse_ttest <- printTTestResult(data$softmaxErr, data$group)
```
```{r, include=FALSE}
uAE_means <- printMeansAndSDs(data$uAE, data$group, 2)
uAE_ttest <- printTTestResult(data$uAE, data$group)
```
```{r, include=FALSE}
uFE_means <- printMeansAndSDs(data$uFE, data$group, 2)
uFE_ttest <- printTTestResult(data$uFE, data$group)
```
```{r, include=FALSE}
u_stats <- printAnovaByEyeTable(data, c('uAE', 'uFE'))
```
```{r, include=FALSE}

softmaxErr_means <- printMeansAndSDs(data$softmaxErr, data$group, 2)
softmaxErr_ttest <- printTTestResult(data$softmaxErr, data$group)

```


Mean (SD) values are shown.

### Calibration parameters

```{r, include=FALSE}
# <!-- delay: -->
# 
# <!--   * `r delay_means[1]` -->
# <!--   * `r delay_means[2]` -->
# <!--     - Amblyopia vs. controls: `r delay_ttest[1]` -->
# <!--   * `r delay_means[3]` -->
# 
# <!-- ```{r, fig.width=5, fig.height=5, echo = FALSE} -->
# <!-- stripchart_w_means(data$delay, data$group, 'delay', c(0,1)) -->
# <!-- ``` -->
```

intercept:

  * `r intercept_means[1]`
  * `r intercept_means[2]`
    - Amblyopia vs. controls: `r intercept_ttest[1]`
  * `r intercept_means[3]`
  
```{r, fig.width=5, fig.height=5, echo = FALSE}
axisVal <- c(floor(min(data$intercept, na.rm=TRUE)), 
             ceiling(max(data$intercept, na.rm=TRUE)))
stripchart_w_means(data$intercept, data$group, 'intercept', axisVal)
```

slope:

  * `r slope_means[1]`
  * `r slope_means[2]`
    - Amblyopia vs. controls: `r slope_ttest[1]`
  * `r slope_means[3]`

  
```{r, fig.width=5, fig.height=5, echo = FALSE}
axisVal <- c(floor(min(data$slope, na.rm=TRUE)), 
             ceiling(max(data$slope, na.rm=TRUE)))
stripchart_w_means(data$slope, data$group, 'slope', axisVal)
```

 fit error (mean trials):

  * `r joyCalErrMean_means[1]`
  * `r joyCalErrMean_means[2]`
    - Amblyopia vs. controls: `r joyCalErrMean_ttest[1]`
  * `r joyCalErrMean_means[3]`
   
   
```{r, fig.width=5, fig.height=5, echo = FALSE}
axisVal <- c(floor(min(data$joyCalErrMean, na.rm=TRUE)*20)/20, 
             ceiling(max(data$joyCalErrMean, na.rm=TRUE)*20)/20)
stripchart_w_means(data$joyCalErrMean, data$group, 'calib. err (mean trials)', axisVal)
```
   
 fit error (individual trials):

  * `r joyCalErrInd_means[1]`
  * `r joyCalErrInd_means[2]`
    - Amblyopia vs. controls: `r joyCalErrInd_ttest[1]`
  * `r joyCalErrInd_means[3]`
   
```{r, fig.width=5, fig.height=5, echo = FALSE}
axisVal <- c(floor(min(data$joyCalErrInd, na.rm=TRUE)*10)/10, 
             ceiling(max(data$joyCalErrInd, na.rm=TRUE)*10)/10)
stripchart_w_means(data$joyCalErrInd, data$group, 'calib. err (indiv. trials)', axisVal)
```
   
    
### Model parameters
  
k~AE~:

  * `r kae_means[1]`
  * `r kae_means[2]`
    - Amblyopia vs. controls: `r kae_ttest[1]`
  * `r kae_means[3]`
   
```{r, fig.width=5, fig.height=5, echo = FALSE}
axisVal <- c(floor(min(data$kAE, na.rm=TRUE)), 
             ceiling(max(data$kAE, na.rm=TRUE)))
stripchart_w_means(data$kAE, data$group, 'kAE', axisVal)
```
 
$\mu$~AE~:

  * `r uAE_means[1]`
  * `r uAE_means[2]`
    - Amblyopia vs. controls: `r uAE_ttest[1]`
  * `r uAE_means[3]`

 
$\mu$~FE~:

  * `r uFE_means[1]`
  * `r uFE_means[2]`
    - Amblyopia vs. controls: `r uFE_ttest[1]`
  * `r uFE_means[3]`
  
$\mu$ ANOVA test: `r u_stats[1]`

```{r, fig.width=5, fig.height=5,echo=FALSE}
axisVal <- c(floor(min(c(data$uAE, data$uFE), na.rm=TRUE)), 
             ceiling(max(c(data$uAE, data$uFE), na.rm=TRUE)))
stripchart_w_means_byeye(data$uAE, data$uFE,
                          data$group, data$group, 'u', axisVal)
```

```{r, include=FALSE}
# <!-- $\sigma$:  -->
# 
# <!--   * `r sigma_means[1]` -->
# <!--   * `r sigma_means[2]` -->
# <!--     - Amblyopia vs. controls: `r sigma_ttest[1]` -->
# <!--   * `r sigma_means[3]` -->
# 
# 
# <!-- ```{r, fig.width=5, fig.height=5, echo = FALSE} -->
# <!-- axisVal <- c(floor(min(data$sigma, na.rm=TRUE)),  -->
# <!--              ceiling(max(data$sigma, na.rm=TRUE))) -->
# <!-- stripchart_w_means(data$sigma, data$group, 'sigma', axisVal) -->
# <!-- ``` -->
```

MSE: 

  * `r mse_means[1]`
  * `r mse_means[2]`
    - Amblyopia vs. controls: `r mse_ttest[1]`
  * `r mse_means[3]`
  

   
```{r, fig.width=5, fig.height=5, echo = FALSE}
axisVal <- c(floor(min(data$softmaxErr, na.rm=TRUE)), 
             ceiling(max(data$softmaxErr, na.rm=TRUE)))
stripchart_w_means(data$softmaxErr, data$group, 'softmaxErr', axisVal)
```
 

