---
title: "Statistics summary: psychophysics from VEP study"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
# setwd("/Users/bear/Downloads/dynamic_contrast/analysis_vep")

library('psych')
library('tidyr')
library('rstatix')
library('lm.beta')
library('kableExtra')
library('effectsize')

# load custom function file
source('r_helper_functions.R')
csvModelFitsPath <- file.path('..',
  'fitdata_vep_psychophysics', 'vep_psychophysics_congruent_fits.csv')
data <- read.csv(csvModelFitsPath)
data$group <- as.factor(data$group)
```

## Participant details
```{r}
Ns <- summary(data$group)
```

Total sample size: `r sum(Ns)`

  * Control n = `r Ns['NS']`
  * Amblyopia n = `r Ns['AM']`
  * Binocular disorder (no amblyopia) n = `r Ns['BD']`
 
## Calibration parameters

   * Calibration range (p.clean_range): `r data$clean_range[1]`
   * Mean good trials per person (p.n_good): `r round(mean(data$n_good),1)` (range: `r min(data$n_good)` to `r max(data$n_good)`)
  
### Delay (in sec):
```{r, fig.width=4, fig.height=4.5}
stripchart_w_means(data$delay, data$group, 'delay', 
                   c(0,ceil_round(max(data$delay),1)),2)
delay_means <- printMeansAndSDs(data$delay, data$group, 2)
delay_ttest <- printTTestResult(data$delay, data$group)
```

**Mean (SD) values:**

   * `r delay_means[1]`
   * `r delay_means[2]`
     - Amblyopia vs. controls: `r delay_ttest[1]`
   * `r delay_means[3]`

 
### Intercept (a):
```{r, fig.width=4, fig.height=4.5}
ylims <- c(floor_round(min(data$intercept, na.rm=TRUE),1),
           ceil_round(max(data$intercept, na.rm=TRUE),1))
stripchart_w_means(data$intercept, data$group, 'intercept (a)', ylims,2)
intercept_means <- printMeansAndSDs(data$intercept, data$group, 2)
intercept_ttest <- printTTestResult(data$intercept, data$group)
```

**Mean (SD) values:**

   * `r intercept_means[1]`
   * `r intercept_means[2]`
     - Amblyopia vs. controls: `r intercept_ttest[1]`
   * `r intercept_means[3]`

### Slope (b):
```{r, fig.width=4, fig.height=4.5}
ylims <- c(floor_round(min(data$slope, na.rm=TRUE),1),
           ceil_round(max(data$slope, na.rm=TRUE),1))
stripchart_w_means(data$slope, data$group, 'slope (b)', ylims,2)
slope_means <- printMeansAndSDs(data$slope, data$group, 2)
slope_ttest <- printTTestResult(data$slope, data$group)
```

**Mean (SD) values:**

   * `r slope_means[1]`
   * `r slope_means[2]`
     - Amblyopia vs. controls: `r slope_ttest[1]`
   * `r slope_means[3]`


### Calibration error (mean across trials):
```{r, fig.width=4, fig.height=4.5}
ylims <- c(0,
           ceil_round(max(data$joyCalErrMean, na.rm=TRUE),3))
stripchart_w_means(round(data$joyCalErrMean,4), data$group, 'joyCalErrMean', ylims,4)
joyCalErrMean_means <- printMeansAndSDs(data$joyCalErrMean, data$group, 4)
joyCalErrMean_ttest <- printTTestResult(data$joyCalErrMean, data$group)
```

**Mean (SD) values:**

   * `r joyCalErrMean_means[1]`
   * `r joyCalErrMean_means[2]`
     - Amblyopia vs. controls: `r joyCalErrMean_ttest[1]`
   * `r joyCalErrMean_means[3]`


### Calibration error (individual trials):
```{r, fig.width=4, fig.height=4.5}
ylims <- c(0,
           ceil_round(max(data$joyCalErrInd, na.rm=TRUE),3))
stripchart_w_means(round(data$joyCalErrInd,4), data$group, 'joyCalErrInd', ylims,4)
joyCalErrInd_means <- printMeansAndSDs(data$joyCalErrInd, data$group, 4)
joyCalErrInd_ttest <- printTTestResult(data$joyCalErrInd, data$group)
```

**Mean (SD) values:**

   * `r joyCalErrInd_means[1]`
   * `r joyCalErrInd_means[2]`
     - Amblyopia vs. controls: `r joyCalErrInd_ttest[1]`
   * `r joyCalErrInd_means[3]`

## Model parameters

### Attenuation (k_AE)
```{r, fig.width=4, fig.height=4.5}
ylims <- c(0,1)
stripchart_w_means(round(data$kAE,4), data$group, 'k(AE)', ylims,2)
kAE_means <- printMeansAndSDs(data$kAE, data$group, 2)
kAE_ttest <- printTTestResult(data$kAE, data$group)
```

**Mean (SD) values:**

   * `r kAE_means[1]`
   * `r kAE_means[2]`
     - Amblyopia vs. controls: `r kAE_ttest[1]`
   * `r kAE_means[3]`

### U values
```{r, fig.width=5, fig.height=4.5}
ylims <- c(floor_round(min(c(data$uAE, data$uFE), na.rm=TRUE),1),
           ceil_round(max(c(data$uAE, data$uFE), na.rm=TRUE),1))

stripchart_w_means_byeye(data$uAE, data$uFE, data$group, data$group,
                         'U', ylims)

uAE_means <- printMeansAndSDs(data$uAE, data$group, 2)
uFE_means <- printMeansAndSDs(data$uFE, data$group, 2)
```
```{r, include=FALSE}
u_stats <- printAnovaByEyeTable(data, c('uAE', 'uFE'))
```

**Mean (SD) values, u_AE:**

   * `r uAE_means[1]`
   * `r uAE_means[2]`
   * `r uAE_means[3]`

**Mean (SD) values, u_FE:**

   * `r uFE_means[1]`
   * `r uFE_means[2]`
   * `r uFE_means[3]`

**$\mu$ ANOVA test:**

   * `r u_stats[2]`
   * `r u_stats[3]`
   * `r u_stats[4]`
   * `r u_stats[5]`
   * `r u_stats[6]`

### Sigma
```{r, fig.width=4, fig.height=4.5}
ylims <- c(floor_round(min(data$sigma, na.rm=TRUE),1),
           ceil_round(max(data$sigma, na.rm=TRUE),1))
stripchart_w_means(data$sigma, data$group, 'sigma', ylims,2)
sigma_means <- printMeansAndSDs(data$sigma, data$group, 2)
sigma_ttest <- printTTestResult(data$sigma, data$group)
```

**Mean (SD) values:**

   * `r sigma_means[1]`
   * `r sigma_means[2]`
     - Amblyopia vs. controls: `r sigma_ttest[1]`
   * `r sigma_means[3]`

### Fit error
```{r, fig.width=4, fig.height=4.5}
ylims <- c(floor_round(min(data$softmaxErr, na.rm=TRUE),1),
           ceil_round(max(data$softmaxErr, na.rm=TRUE),1))
stripchart_w_means(data$softmaxErr, data$group, 'softmaxErr', ylims,2)
softmaxErr_means <- printMeansAndSDs(data$softmaxErr, data$group, 3)
softmaxErr_ttest <- printTTestResult(data$softmaxErr, data$group)
```

**Mean (SD) values:**

   * `r softmaxErr_means[1]`
   * `r softmaxErr_means[2]`
     - Amblyopia vs. controls: `r softmaxErr_ttest[1]`
   * `r softmaxErr_means[3]`

